---
title: "Databricks Demo - Iris Data ML"
output: html_document
---

## Setup

- Install packages
```{r setup, include=FALSE}
#install.packages("sparklyr")
#install.packages("dplyr")
```

- Load the libraries
```{r message=FALSE}
library(sparklyr)
library(SparkR)
library(dplyr)
library(tidyr)
library(ggplot2)
```

- Connect to Databricks with sparklyr
```{r}
sparkR.session()
sc <- spark_connect(method = "databricks")
```

## Basic Cheatsheet ML - Iris Data Demo

- Copy iris data to Spark memory
- Split data into train/test frames
- Create metadata for each new frame
```{r}
import_iris <- copy_to(sc, iris, "spark_iris", overwrite = TRUE)
partition_iris <- sdf_partition(import_iris, training=0.5, testing=0.5)
sdf_register(partition_iris, c("spark_iris_training", "spark_iris_test"))
```

- Use Spark ML to create a decision tree model
```{r}
# Create a reference pointer in R for selected training data cols
tidy_iris <- tbl(sc, "spark_iris_training") %>%
  select(Species, Petal_Length, Petal_Width)

# Build a Spark ML model
model_iris <- tidy_iris %>%
  ml_decision_tree(response = "Species",
                   features = c("Petal_Length", "Petal_Width"))
```

- Use `sdf_predict` and the decision tree model to make predictions for the test data
- Collect the test predictions into R and make a plot 
```{r}
# Create a reference pointer in R for the test data
test_iris <- tbl(sc, "spark_iris_test")

# Generate and collect predictions
pred_iris <- sdf_predict(test_iris, model_iris) %>%
  collect

# Plot the predictions in R, label all incorrect
pred_iris %>%
  select(Petal_Length, Petal_Width, Species, label, prediction) %>%
  mutate(correct_prediction = ifelse(test = (label == prediction), yes = 1, no = 0)) %>%
  ggplot(aes(Petal_Length, Petal_Width, col=correct_prediction)) +
  geom_point()
```

